Make any stupid plot you want

### 2020-12-10 draft/sections/math.tex
start of nu

\subsubsection{Marks}
%% diagram of connected components/line thing 11-19-20 notes
Bertin describes a location on the plane as the signifying characteristic of a point, measurable length as the signifying characteristic of a line, and measurable size as the signifying characteristic of an area and that in display (pixel) space these are marks \cite{bertinIIPropertiesGraphic2011,carpendaleVisualRepresentationSemiology}. 
\begin{equation}
\begin{tikzcd}
    H \arrow[r, shift left] & S \arrow[l, "\rho(\xi^{-1}(J))", shift left] \arrow[rr, "\xi(s)", shift left] &  & J_{k} =  \{j \in K| \exists \Gamma \text{ s.t. } \Gamma(0)=k \text{ and }\Gamma(1)=j\} \arrow[ll, "\xi^{-1}(J)", shift left]
\end{tikzcd}
\label{eq:mark}
\end{equation}

@@

\subsubsection{Channels}
The function $rho: S \rightarrow H$ is composed of subfunctions that are dependent on the prerender fiber $D$. In the case of a screen
\begin{equation}
    \rho (\alpha, \beta) = (\rho_X(\alpha, \beta), \rho_Y(\alpha, \beta), \rho_Z(\alpha, \beta), \rho_B(\alpha, \beta), \rho_G(\alpha, \beta), \rho_B(\alpha, \beta), \rho_A(\alpha, \beta))
\end{equation}

where $(\alpha, \beta)$ are coordinates on $S$. The function $Q$

\begin{equation}
    \begin{tikzcd}
        \Gamma(\theta) \arrow[rr, "{Q(\nu_{0}(c),\ldots,\nu_n(c))}"] &  & {\rho_X, \rho_Y, \rho_Z, \rho_R, \rho_B, \rho_G, \rho_A}
    \end{tikzcd}
\end{equation}

>>>>

As described in section~\ref{sec:display}, $rho: S \rightarrow H$ is composed of subfunctions that are dependent on the prerender fiber $D$. In the case of a screen
\begin{equation}
    \rho (\alpha, \beta) = (\rho_X(\alpha, \beta), \rho_Y(\alpha, \beta), \rho_Z(\alpha, \beta), \rho_B(\alpha, \beta), \rho_G(\alpha, \beta), \rho_B(\alpha, \beta), \rho_A(\alpha, \beta))
\end{equation}

where $(\alpha, \beta)$ are coordinates on $S$. The mapping $Q: \Gamma(\tau) \rightarrow D$ builds $\rho$ functions on $S$ by compositing $\nu: c \mapsto v \subset {x,y,z,r,g,b,a}$ functions that map data in some field $c$ to a subset of display variables.

\begin{equation}
    \begin{tikzcd}
        \Gamma(\tau) \arrow[rr, "{Q(\nu_{0}(c),\ldots,\nu_n(c))}"] &  & {\rho_X, \rho_Y, \rho_Z, \rho_R, \rho_B, \rho_G, \rho_A}
    \end{tikzcd}
    \label{eq:Q}
\end{equation}

$Q$ composites $\nu$ functions because multiple mappings can target the same field in $D$, for example y position and linewidth will concurrently affect where a pixel is drawn on screen.

\subsubsection{Marks}
Bertin describes a location on the plane as the signifying characteristic of a point, measurable length as the signifying characteristic of a line, and measurable size as the signifying characteristic of an area and that in display (pixel) space these are marks \cite{bertinIIPropertiesGraphic2011,carpendaleVisualRepresentationSemiology}. 
\begin{equation}
\begin{tikzcd}
    H \arrow[r, shift left] & S \arrow[l, "\rho(\xi^{-1}(J))", shift left] \arrow[rr, "\xi(s)", shift left] &  & J_{k} =  \{j \in K| \exists \Gamma \text{ s.t. } \Gamma(0)=k \text{ and }\Gamma(1)=j\} \arrow[ll, "\xi^{-1}(J)", shift left]
\end{tikzcd}
\label{eq:mark}
\end{equation}

@@

\subsubsection{Channels}
Visual channels are mappings from data into visual space, for example distinguishing categories by coloring them differently  \cite{bertinIIPropertiesGraphic2011,munznerMarksChannels}. Channels are an example of $\nu: c \mapsto d \in D$, which are the mappings from data $r \in \Gamma(\tau)$ to some part of the prerender fiber $D$. the $\nu$ functions can target only one field in $D$, such as $X$, or multiple such as $R,G,B$.
